When Do You Repeat Yourself?\\ Voices from the Trenches of Linux Kernel Maintainers on Code Duplication

### 2025-10-27 paper/techdebt2026/techdebt.tex
techdebt2026: techdebt: change takeaway 4 to use correct reference
As pointed out in a TODO, the reference being used to base the claim
that jumping across code fragments increases cognitive load was
not the best one, and we needed to resolve the "base" reference the one
used cited. After some research, we settled with the Sillito et. al [1]
reference, as it better fits what we are trying to claim.

[1]: https://doi.org/10.1145/1181775.1181779

Signed-off-by: David Tadokoro <davidbtadokoro@usp.br>

%TODO Na citação abaixo, trazida pelo Arthur, pensar se não vale colocar as
%referências base do paper do Lanza: ``Developers need to mentally reconstruct
%the role and behavior of a class from scattered fragments of code [8],
%presented as one page of text at a time. This process is cognitively demanding
%[9], slow, and error-prone, especially in large systems with many
%interdependent components [10].''
%
% Referências do paper do Lanza para esse trecho:
%[8] M.-A. Storey, “Theories, methods and tools in program comprehension:
%Past, present and future,” in Proceedings of IWPC 2005. IEEE, 2005,
%pp. 181–191.
%[9] J. Sillito, G. C. Murphy, and K. De Volder, “Questions programmers
%ask during software evolution tasks,” in Proceedings FSE 2006. ACM,
%2006, pp. 23––34.
%[10] G. C. Murphy, D. Notkin, and K. Sullivan, “Software reflexion models:
%Bridging the gap between source and high-level models,” in Proceedings
%of FSE 1995. ACM, 1995, pp. 18–28.
\begin{highlight-box}{Takeaway T4 (Cognitive Load)}
  Duplications that made it possible to read the code without needing to jump
  to the function definition (to see its behavior) or the function call (to see
  its concrete parameters) were justifiable to reduce cognitive load when
  parsing through the code~\cite{skylines-cognitive-load}.
\hfill\\

>>>>

\begin{highlight-box}{Takeaway T4 (Cognitive Load)}
  Needing to jump to a function definition (to see its behavior) or a function
  call (to see its concrete parameters) in order to understand code is a
  cognitively demanding task for developers~\cite{questions-programmers-ask}.
  Duplications that avoided this were justifiable to reduce cognitive load when
  parsing through the code.
\hfill\\
